---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
# Please put your title here to include it in the file below.
Title <- "CESAB datatoolbox workshop exercices"
```

# datatoolboxexos

This repository contains the code and data I used during the datatoolbox CESAB workshop exercices. The courses and exercices of the workshop are obtainable [>here<](https://github.com/FRBCesab/datatoolbox).

### How to cite

Please cite this compendium as:

> Authors, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r Title`_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

## Contents

The [**exercices**](exercices/) directory contains:

  - [::spiral\_notepad:: exo_dplyr](/exercices/exo_dplyr.Rmd)
  - [::spiral\_notepad:: exo_2](/exercices/exo_2.Rmd)
  
R Markdown source documents for the exercice. Includes code to reproduce the figures and tables generated by the analyses. They also have rendered versions, `.md` and `html` suitable respectively for reading on github and in a web browser.

The [**data**](data/) directory contains the Data used in the analysis. There is a `README` in that directory that describes the Data.

## How to run it ?

This research compendium has been developed using the statistical programming
language R. To work with the compendium, you will need
installed on your computer the [R software](https://cloud.r-project.org/)
itself and optionally [RStudio Desktop](https://rstudio.com/products/rstudio/download/).

You can download the compendium as a zip from from this URL:
[master.zip](/archive/master.zip). After unzipping:

- open the `.Rproj` file in RStudio

- open `make.R` and source it to ensure you have the packages this analysis depends on (also listed in the [DESCRIPTION](/DESCRIPTION) file) and produce the reports for all the exercercices.

### Licenses

**Text and figures :**  [CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/)

**Code :** See the [DESCRIPTION](DESCRIPTION) file

**Data :** [CC-0](http://creativecommons.org/publicdomain/zero/1.0/) attribution requested in reuse

## Session Info

```{r}
utils::sessionInfo()
```

